\bibliographystyle{plain}
\begin{thebibliography}{9}
 \bigskip
 \barra
 \bigskip

\bibitem{ref1}
S. Cordero, et al., ''Review: Site-Bond Network Modeling of Disordered Porous Media,`` vol. 21, pp. 101–116, 2004.

\bibitem{ref2}
S. Cordero, F. Rojas, J.L. Riccardo, ''Simulation of three-dimensional porous networks,`` Colloids and Surfaces A: Physicochemical and Engineering Aspects, vol. 187–188, pp. 425-438, 2001. 

\bibitem{ref3}
G. Román, F. Rojas, M. Aguilar, S. Cordero, M.A. Castro, ''In-silico simulation of porous media: Conception and development of a greedy algorithm,`` Microporous and Mesoporous Materials, vol. 137, pp. 18-31, 2011. 

\bibitem{ref4}
J. Matadamas, G. Román-Alonso, F. Rojas, M. Castro, A. Boukerche, M. Aguilar, S. Cordero, ''Parallel Simulation of Pore Networks Using Multicore CPUs”, IEEE Transactions on Computers, 2012. 

\bibitem{ref5}
''Refinements of the Twofold Description of Porous Media``, Mayagoitia V., Rojas F., Kornhauser I.,Zgrablich G., Faccio R.J., Gilot B., and Guiglion C., Langmuir, 12, 211-216, 1996. 

\bibitem{ref6}
B. Chapman, G. Jost, R. van der Pas, ''Using OpenMP: Portable Shared Memory Parallel Programming,`` The MIT Press, pp. 384, 2007. 

\bibitem{ref7}
C.H. Moreno, F. Rojas, G. Román, S. Cordero, M.A. Castro, M. Aguilar, ''A Parallel Simulator for Mercury (Hg) Porosimetry,`` M. Ropo et al. (Eds.): EuroPVM/MPI 2009. LNCS, Springer, vol. 5759, pp. 294–304, 2009.

\bibitem{ref8}
M. Sahimi, ''Flow phenomena in rocks: from continuum models to fractals, percolation, cellular automata, and simulated annealing,`` Rev. Mod. Phys. 1993, 65(4), 1393-1534. 

\bibitem{ref9}
U. Gil-Cruz, M. A. Balderas-Altamirano, S. Cordero-Sánchez, ''Textural study of simulated dimorphic porous substrates,`` Colloids Surf. A, 2010, 357(1-3), 8492UTF$\{$2013$\}$90. 

\bibitem{ref10}
M.D. Kalugin, and A.V. Teplukhin, ''Parallel Monte Carlo study on caffeine-DNA interaction in aqueous solution``, IPDPS, pp.1-8, 2009 IEEE International Symposium on Parallel $\&$ Distributed IP Processing, 2009. 

\bibitem{ref11}
V. Mayagoitia, F. Rojas, I. Kornhauser and H. Pérez-Aguilar. ''Modeling of Porous Media and Surface Structures: Their True Essence as Networks,`` Langmuir. vol. 13, pp. 1327-1331 1997.

\bibitem{ref12} T. Sterling. ''Beowulf Cluster Computing with Linux,`` MIT Press, Cambridge, 2001.

\bibitem{ref13}
David R. Butenhof, ''Programming With Posix Threads,`` Addison-Wesley, 1997.

\bibitem{ref14}
H. Chung, C. Chang, H. Hsiao and Y. Chao, ''The Load Rebalancing Problem in Distributed File Systems,`` Cluster Computing (CLUSTER), IEEE International Conference on, pp.117,125, 24-28 Sept. 2012.

\bibitem{ref15}
M. Newman and G. Barkema, ''Monte Carlo Methods in Statistical Physics,`` Oxford University Press, Chap. 2, pp. 31-44, 2007.

\bibitem{ref16}
A. Gonz\'alez-M\'endez, G. Rom\'an-Alonso, F. Rojas-Gonz\'alez, M.A. Castro-Garc\'ia, M. Aguilar-Cornejo, and S. Cordero-S\'anchez;
''Construction of Porous Networks subjected to Geometric Restrictions by using OpenMP''; IEEE 28th
International Parallel \& Distributed Processing Symposium Workshops, Phoenix, USA, pp. 1189-1197, 2014.

%\bibitem{ref17}
%Fernando Rojas-Gonz\'alez, Graciela Rom\'an-Alonso, Salom\'on Cordero-S\'anchez, Miguel Alfonso Castro-Garc\'ia, Manuel Aguilar-Cornejo and Jorge Matadamas Hern\'andez; Book Chapter 1: ''On The Conception and Assessment of Mesopore Networks: Development of Computer Algorithms''; Nova Science Publishers, Inc. pp.1-28, to appear, 2014.

\bibitem{ref17}
Fernando Rojas-Gonz\'alez, Graciela Rom\'an-Alonso, Salom\'on Cordero-S\'anchez, Miguel Alfonso Castro-Garc\'ia, Manuel Aguilar-Cornejo and Jorge Matadamas Hern\'andez; Book "Comprehensive Guide for Mesoporous Materials"; Chapter : ''On The Conception and Assessment of Mesopore Networks: Development of Computer Algorithms''; Nova Science Publishers, Inc. vol. 3, pp.1-28, to appear (2o trimestre de 2015), ISBN: 978-1-63463-318-5, 2015.

\bibitem{ref18}
S. Cordero, F. Rojas, and J.L. Riccardo; "Simulation of three-dimensional porous networks Colloids and Surfaces A: Physicochemical and Engineering Aspects", 187-188 (2001), pp.425- 438, 2001.


%\bibitem{mchybrid}
%G. Tang, K. Li, H. Chen and J. Du, ''A Hybrid Parallel TRidiagonal Solver on Multi-Core Architectures,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.604-613, 19-23 Mayo 2014.
%
%\bibitem{mcmulticore}
%M. Mezmaz, R. Leroy, N. Melab and D. Tuyttens, ''A Multi-Core Parallel Branch-and-Bound Algorithm Using Factorial Number System,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium, pp.1203-1212, 19-23 Mayo 2014.
%
%\bibitem{mcdynamically}
%S. Donfack, S. Tomov and J. Dongarra, ''Dynamically balanced synchronization-avoiding LU factorization with multicore and GPUs,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.958-965, 19-23 Mayo 2014.
%
%\bibitem{mcopenmpt}
%A. Qawasmeh, A. Malik and B. Chapman, ''OpenMP Task Scheduling Analysis via OpenMP Runtime API and Tool Visualization,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.1049-1058, 19-23 Mayo 2014.
%
%\bibitem{mcscheduling}
%L. Chen, X. Huo, G. Agrawal, ''Scheduling Methods for Accelerating Applications on Architectures with Heterogeneous Cores,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.48-57, 19-23 Mayo 2014.
%
%\bibitem{sibalancing}
%C. Xu, L. Zhang, X. Deng, J. Fang, G. Wang, W. Cao, Y. Che, Y. Wang and W. Liu, ''Balancing CPU-GPU Collaborative High-order CFD Simulations on the Tianhe-1A Supercomputer,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium, pp.725-734, 19-23 Mayo 2014.
%
%\bibitem{sicloud}
%A. Paya and Dan C. Marinescu, ''Cloud-based Simulation of a Smart Power Grid
%,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.875-884, 19-23 Mayo 2014.
%
%\bibitem{siconstructing}
%J. Zola, ''Constructing Similarity Graphs from Large-scale Biological Sequence Collections,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.500-507, 19-23 Mayo 2014.
%
%\bibitem{sikdtree}
%K. Kofler, D. Steinhauser, B. Cosenza, I. Grasso, S. Schindler and T. Fahringer , ''Kd-tree Based N-Body Simulations with Volume-Mass Heuristic on the GPU,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.1256-1265, 19-23 Mayo 2014.
%
%\bibitem{silscale}
%X. Liu and E. Chow, ''Large-Scale Hydrodynamic Brownian Simulations on Multicore and Manycore Architectures,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium, pp.563-572, 19-23 Mayo 2014.
%
%\bibitem{sinfusion}
%N. Fujita, H. Nuga, T. Boku and Y. Idomura, ''Nuclear Fusion Simulation Code Optimization and Performance Evaluation on GPU Cluster,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.1266-1274, 19-23 Mayo 2014.
%
%\bibitem{siovercomming}
%J. Yeom, A. Bhatele, K. Bisset, E. Bohm, A. Gupta, L. Kale, M. Marathe, D. Nikolopoulos, M. Schulz and L. Wesolowski, ''Overcoming the Scalability Challenges of Epidemic Simulations on Blue Waters,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium, pp.755-764, 19-23 Mayo 2014.
%
%\bibitem{siprocess}
%J. Li, A. Salighehdar, N. Ganesan ''Process Simulation of Complex Biochemical Pathways in Explicit 3D Space Enabled by Heterogeneous Computing Platform,`` 2014 IEEE 28th International Parallel $\&$ Distributed Processing Symposium Workshops, pp.528-535, 19-23 Mayo 2014.

\end{thebibliography}